Paper_analyses

### 2021-07-27 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

@@

?annotate
```

I think this clustering might

@@

```{r}
# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05
?p.adjust
timecourse_60bin_result_df_vel$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel$p_ar, method = "holm")
timecourse_60bin_result_df_vel$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_adj<.05, TRUE, FALSE)

@@

```{r}
#  let's use the order arousal, valence, arousal x valence brightness
timecourse_60bin_result_df_vel %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  #change the order of the coloring variable here and the name of legends
  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+

  scale_color_brewer(palette = "Dark2")
    # scale_color_manual(values=c("#1B9E77", "#D95F02", "#7570B3", "#E7298A"))+
  # use hom correction for significance

    # brighteness
    timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_br_adj_TRUE == TRUE]

@@

>>>>

?p.adjust

# flad when 3 consecutive rows have a p <.05
require(zoo)

# rle performs lenght encoding
rletest<- rle(timecourse_60bin_result_df$p_ar<.05)
?rle

  (rletest$lengths[rletest$lengths > 3 & rletest$values== TRUE]) # length of each sequence

# To get the vector with only a sequence of "TRUE" you can try

rletest$values[rletest$values != TRUE] <- 0
timecourse_60bin_result_df$p_ar_3below.5<- rep(rletest$values,  rletest$lengths)

table(timecourse_60bin_result_df$p_ar_3below.5)
?p.adjust

timecourse_60bin_result_df%>%
  group_by(p_ar_3below.5)%>%
  mutate(p_ar_adj_clust= p.adjust(p_ar, method = "holm"))

timecourse_60bin_result_df %>%
  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%

@@

split neutral positive and negative usign ground

colnames(tmp.df4_full_stim_downs_jun2021_60bins)

?p.adjust

# flad when 3 consecutive rows have a p <.05
require(zoo)

# rle performs lenght encoding
rletest<- rle(timecourse_60bin_result_df$p_ar<.05)
?rle

  (rletest$lengths[rletest$lengths > 3 & rletest$values== TRUE]) # length of each sequence

# To get the vector with only a sequence of "TRUE" you can try

rletest$values[rletest$values != TRUE] <- 0
timecourse_60bin_result_df$p_ar_3below.5<- rep(rletest$values,  rletest$lengths)

table(timecourse_60bin_result_df$p_ar_3below.5)
?p.adjust

timecourse_60bin_result_df%>%
  group_by(p_ar_3below.5)%>%
  mutate(p_ar_adj_clust= p.adjust(p_ar, method = "holm"))

timecourse_60bin_result_df %>%
  mutate(test=rollapply(p_ar, width=3, max, align="left", fill=NA, na.rm=TRUE))%>%

@@

```{r}
# adjust p values and tag as TRUE whenevee there is at least 3 consecutive p values below .05

mutate(ANC=rollapply(ANC, width=3, max, align="left", fill=NA, na.rm=TRUE)) %>%
  filter(ANC >= 0.5) %>%  
  filter(row_number() == 1)

```{r}
timecourse_60bin_result_df_vel$p_ar_adj<- p.adjust(timecourse_60bin_result_df_vel$p_ar, method = "holm")
timecourse_60bin_result_df_vel$p_ar_adj_TRUE<- if_else(timecourse_60bin_result_df_vel$p_ar_adj<.05, TRUE, FALSE)

@@

View(timecourse_60bin_result_df_vel)
#  let's use the order arousal, valence, arousal x valence brightness

plots_timecourse$eff_size_pup_velocity<-
timecourse_60bin_result_df_vel %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  #change the order of the coloring variable here and the name of legends
  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+

    # brighteness
    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_br_adj_TRUE == TRUE]

    annotate(geom = 'rect', # use annotate instead of geom_rect, as it is more flexible
             xmin = .37, # got these values from the data-frame. need to fidn a way to automate this
                xmax = .81,
                ymin = -2.03+(sf*1.2), # if I ever need to change this, use the scaling factor sf
                ymax = -2+.1+.01+(sf*1.2),
                fill =  "#E7298A" , alpha = .5)+

      # annotate("text", 
      #           x = (1+5.4)/2,
      #           y = ((-2) +(-2+.1))/2+(sf*.3),
      #           label = "brightness") +

@@

    # timecourse_60bin_result_df$p_ar_adj

    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_ar_adj_TRUE == TRUE]

    # timecourse_60bin_result_df_vel$timebins

    annotate(geom = 'rect', 
              xmin = 1.028329,
                xmax = 1.028329+.1,
                ymin = -2.03+.1+.1+.1+.1+(sf*1.2),
                ymax = -2+.1+.1+.1+.1+.1+.01+(sf*1.2),
                fill = "#1B9E77", alpha = .5)+
        # annotate("text", 
        #           x = (1+5.4)/2,
        #         y = ((-2+.1+.1+.1+.1) +(-2+.1+.1+.1+.1+.1))/2+(sf*.3),
        #          label = "arousal") +

    # arousal-valence
   # timecourse_60bin_result_df$p_ar_vl_adj
    # timecourse_60bin_result_df_vel$timebins[timecourse_60bin_result_df_vel$p_ar_vl_adj_TRUE == TRUE]
       annotate(geom = 'rect', 
                xmin = 5.5730353,
                xmax = 5.5730353+.1,
                ymin = -2.03+.1+.1+(sf*1.2),
                ymax = -2+.1+.1+.1+.01+(sf*1.2),

                fill ="#7570B3", alpha = .5, label = "text")+

  # annotate("text", 
  #               x = (1+5.4)/2,
  #               y = ((-2+.1+.1) +(-2+.1+.1+.1))/2+(sf*.3),
  #               label = "arousal x valence") +
        xlab("Time (s)")+
    ylab("Effect size")+
    xlab("Time (s)")+
    ylab("Effect size")

plots_timecourse$eff_size_pup_velocity
# need to rename the label legends

# Edit legend title and labels
plots_timecourse$eff_size_pup_velocity

plots_timecourse$eff_size_pup_velocity + 
  p$graphstyle +
    guides(colour = guide_legend(override.aes = list(size=2)))+ #the line size of the legend tends to be smaller in print
  scale_x_continuous(limits = c(0,6), breaks = c(0,2,4,6))+
  scale_y_continuous(limits = c(-1,1.5), breaks = c(-0.5, 0,0.5,1))
